\Large\textbf{Preparation GUIDE for Initial-Submission Manuscript}\\~\\ \large\textbf{ Preparation of Papers in Two-Column Format\\ for the ASP-DAC 2014 (\LaTeX2e version)}

### 2013-06-25 exps.tex
first commit
table

\section{Introducing delays in SystemJ}
\label{sec:intr-delays-syst}

>>>>

\section{Experimental results}
\label{sec:experimental-results}

\begin{center}
\scalebox{0.9}{
\begin{tabular}{|c| c | c | c | c | c | c | c |}
	\cline{4-8}
	\multicolumn{3}{c|}{}											& HRTCS 		& Motor 		  & Robot 			  & AECS/CD1  		   & AECS/CD2\\ \hline
	\multirow{12}{*}{JOP} 		& \multicolumn{2}{|c|}{BCRT} 		&0.0334 ms 		& 0.0361 ms		  & 0.0325 ms		  & 0.1683 ms		   & 0.1881 ms\\ \cline{2-8}   
								& \multicolumn{2}{|c|}{WCRT} 		&0.1120 ms 		& 0.1116 ms		  & 0.0601 ms		  & 0.7147 ms		   & 1.0115 ms\\ \cline{2-8} 
								& \multirow{2}{*}{Delay 1}	 & M..N &50.3-200.3 ms 	& 2.4-7.4772 ms	  & 1230-2274.0263 ms & 10000-42473.2197 ms& 10000-53772.0045 ms \\ \cline{3-8} 
								&			   & d			 		&1506-1787  	& 67 			  & 37861			  & 59427		       &53160\\ \cline{2-8}
								& \multirow{2}{*}{Delay 2}	 & M..N & 	N/A 		& 1.667-5.2452 ms & N/A				  & N/A 			   &10000-53772.0045 ms\\ \cline{3-8} 
								&			   & d			 		& 	N/A	 		& 47			  & N/A				  & N/A       		   &53160\\ \cline{2-8}
								& \multirow{2}{*}{Delay 3}	 & M..N & 	N/A	 		& 0.05-0.2232 ms  & N/A				  & N/A       		   &N/A\\ \cline{3-8} 
								&			   & d			 		& 	N/A	 		& 2		      	  &	N/A				  & N/A       		   &N/A\\ \cline{2-8}
								& \multirow{2}{*}{Delay 4}	 & M..N & 	N/A	 		& 0.3-1.0044 ms   & N/A				  &	N/A       		   &N/A\\ \cline{3-8} 
								&			   & d				 	& 	N/A	 		& 9				  & N/A				  &	N/A      		   &N/A\\ \cline{2-8}
								& \multirow{2}{*}{Delay 5}	 & M..N & 	N/A	 		& 0.733-2.3436 ms & N/A				  &	N/A      		   &N/A\\ \cline{3-8} 
								&			   & d			 		& 	N/A	 		& 21 			  &	N/A				  & N/A      		   &N/A\\ \hline
	\multirow{12}{*}{TP-JOP} 	& \multicolumn{2}{|c|}{BCRT} 		&0.0028 ms 		& 0.0060 ms		  & 0.0011 ms		  & 0.0532 ms		   & 0.0292 ms\\ \cline{2-8}   
								& \multicolumn{2}{|c|}{WCRT} 		&0.0329 ms 		& 0.0393 ms		  & 0.0361 ms		  & 0.5072 ms		   & 0.8388 ms\\ \cline{2-8} 
								& \multirow{2}{*}{Delay 1}	 & M..N &50.3-600.3 ms 	& 2.4-15.6265 ms  & 1230-42317.8276 ms& 10000-95358.8578 ms& 10000-287757.9834 ms \\ \cline{3-8} 
								&			   & d			 		&18209-18232 	& 398 			  & 1171429			  & 188015		       &343054\\ \cline{2-8}
								& \multirow{2}{*}{Delay 2}	 & M..N & 	N/A 		& 1.667-10.8757 ms& N/A				  & N/A 			   &10000-287757.9834 ms\\ \cline{3-8} 
								&			   & d			 		& 	N/A	 		& 277			  & N/A				  & N/A       		   &343054\\ \cline{2-8}
								& \multirow{2}{*}{Delay 3}	 & M..N & 	N/A	 		& 0.05-0.3534 ms  & N/A				  & N/A       		   &N/A\\ \cline{3-8} 
								&			   & d			 		& 	N/A	 		& 9		      	  &	N/A				  & N/A       		   &N/A\\ \cline{2-8}
								& \multirow{2}{*}{Delay 4}	 & M..N & 	N/A	 		& 0.3-1.9631 ms   & N/A				  &	N/A       		   &N/A\\ \cline{3-8} 
								&			   & d				 	& 	N/A	 		& 50			  & N/A				  &	N/A      		   &N/A\\ \cline{2-8}
								& \multirow{2}{*}{Delay 5}	 & M..N & 	N/A	 		& 0.733-4.79 ms   & N/A				  &	N/A      		   &N/A\\ \cline{3-8} 
								&			   & d			 		& 	N/A	 		& 122 			  &	N/A				  & N/A      		   &N/A\\ \cline{2-8}
	\hline
\end{tabular}
}
\end{center}

aa
